---
title: "Statistical inference with the [GSS](http://gss.norc.org/) data"
bibliography: ["proj2.bib", "PackagesUsed.bib"]
output: 
    bookdown::html_document2
date: 'Last compiled: `r format(Sys.time(), "%B %d, %Y")`'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment = NA, fig.align = "center", fig.height = 3, fig.width = 3, message = FALSE, warning = FALSE)
```

## Setup {-}

### Packages and Reproducibility {-}

Create a vector `PackagesUsed` that contains the names of the packages you will use in your project.  Use the function `write_bib()` from the package `knitr` to create a  `*.bib` file for `PackagesUsed` named `PackagesUsed.bib`.  Your code may look similar to what is below.  Delete these notes before turning in your project.

    `r ''````{r, packages, echo = FALSE, message = FALSE, results = 'hide'}
    PackagesUsed <- c("ggplot2", "knitr", "rmarkdown", "dplyr", "bookdown")
    # Write bib information
    knitr::write_bib(PackagesUsed, file = "./PackagesUsed.bib")
    ```

```{r, packages, echo = FALSE, message = FALSE, results = 'hide'}
PackagesUsed <- c("DT", "ggplot2", "knitr", "rmarkdown", "dplyr", "bookdown")
# Write bib information
knitr::write_bib(PackagesUsed, file = "./PackagesUsed.bib")
```

**Example---edit as needed:**  In this project, the `dplyr` package by @R-dplyr is used to explore the data.  Visualization of the data 
is accomplished with the `ggplot2` package created by @R-ggplot2. The data is from @gss.  This document is written with R Markdown using the `rmarkdown`, `knitr`, and `bookdown` packages written by @R-rmarkdown, @R-knitr, and @R-bookdown,  respectively.  


```{r load-packages, message = FALSE}
# load all packages used
library(ggplot2)
library(dplyr)
```

#### Load data {-}


Make sure your data (`gss.RData`) and your R Markdown files are in the same directory. When loaded,
your data file will be called `gss`. If you use additional sources, you will need to add them to the `proj2.bib` file and cite them in the project. Delete this paragraph before you submit your project. 

```{r load-data}
load("gss.RData")
```

#### Figure and Table Captions {-}

Label all Figures and Tables, and then refer to them using the syntax "Figure `\@ref(fig:labelname)`" or "Table `\@ref(tab:labelname).`"  [Bookdown: Authoring Books with R Markdown](https://bookdown.org/yihui/bookdown/) is the definitive reference for the syntax used to label Figures and Tables. 

A few examples labeling Figures and Tables follow.

    `r ''````{r, sp1, fig.cap = "Scatterplot of `dist` versus `speed`", echo = FALSE}
    ggplot(data = cars, aes(x = speed, y = dist)) + 
      geom_point(color = "lightblue") + 
      theme_bw()
    ```

```{r, sp1, fig.cap = "Scatterplot of `dist` versus `speed`", echo = FALSE}
ggplot(data = cars, aes(x = speed, y = dist)) + 
  geom_point(color = "lightblue") + 
  theme_bw()
```
 
To refer to Figure \@ref(fig:sp1), use the syntax `\@ref(fig:sp1)`. Figure \@ref(fig:sp1) shows a scatter plot of distance *versus* speed for the `cars` data frame. 

```{r, MS}
T1 <- xtabs(~race + sex, data = gss)
knitr::kable(T1, caption = "Something descriptive here", booktabs = TRUE)
```

Table \@ref(tab:MS) is a contingency table of race and gender.  Table \@ref(tab:TAB2) shows formatted regression output.

```{r, TAB2}
mod <- lm(dist ~ speed, data = cars)
knitr::kable(coef(summary(mod)), caption = "Sample regression coefficients", booktabs = TRUE)
```

```{r, SS, fig.cap = "Another caption you should complete", fig.width = 4}
ggplot(data = gss, aes(x = sex, fill = race)) + 
   geom_bar(position = "fill") +
   theme_bw()
```

Figure \@ref(fig:SS) shows the proportion of...


Delete the **Figure and Table Captions** section before you submit your project. 

* * *

## Part 1: Data {-}


* * *

## Part 2: Research question {-}



* * *

## Part 3: Exploratory data analysis {-}

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button (green button with orange arrow) above. Make sure that your code is visible
in the project you submit. Delete this note before you submit your work.

* * *

## Part 4: Inference {-}

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button (green button with orange arrow) above. Make sure that your code is visible
in the project you submit. Delete this note before you submit your work.

## References